---
title: My Tastes
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
source('setup.R')

```

Danceability {data-orientation=rows}
================================================================================


Row {data-height=500}
--------------------------------------------------------------

### dist {.no-title}

```{r}
feature_charts[[feature]]
```



Row {data-height=200}
--------------------------------------------------------------------------------


### Least danceable track

```{r}
track <- track_features$id[which.min(track_features[[feature]])]
track <- my_top_tracks %>% filter(id == track) %>% slice(1)
artist <- get_artist(track$artists[[1]]$id)

```

Danceability: `r head(track_features[[feature]][track_features$id == track$id], 1)`

Track: [`r track$name`](`r track$external_urls.spotify`)

Artist: [`r track$artists[[1]]$name`](`r track$artists[[1]]$external_urls.spotify`)

Album: [`r track$album.name`](`r track$album.external_urls.spotify`)

### Artist {.no-title}

![](`r artist$images[2,2]`)


### Artist {.no-title}

```{r}
track <- track_features$id[which.max(track_features[[feature]])]
track <- my_top_tracks %>% filter(id == track) %>% slice(1)
artist <- get_artist(track$artists[[1]]$id)
```


![](`r artist$images[2,2]`)

### Most danceable track

Danceability: `r head(track_features[[feature]][track_features$id == track$id], 1)`

Track: [`r track$name`](`r track$external_urls.spotify`)

Artist: [`r track$artists[[1]]$name`](`r track$artists[[1]]$external_urls.spotify`)

Album: [`r track$album.name`](`r track$album.external_urls.spotify`)

Row {data-height=100}
--------------------------------------------------------------------------------

### Description

`r features$description[features$feature == feature]`
